How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-24 tse-paper/content.tex
Inline abstract

\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
2}}
What are the comparative strengths and weaknesses
of promising build log analysis techniques?
\end{simplebox}

@@

This lead us to the following research questions:
\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ1:} What are the state-of-the-research
techniques to analyze build logs?}
\begin{itemize}[leftmargin=2cm]
  \item[\textbf{RQ1.1:}] Which information is targeted?
  \item[\textbf{RQ1.2:}] Which techniques are used?
  \item[\textbf{RQ1.3:}] Which build logs are analyzed?
\end{itemize}
\end{simplebox}

@@

% TODO: draw a conclusion together with figure 5: if reuse were higher,
%lots of effort could be saved?
We observed very little reuse of build log analysis tools.
This can stem from the
high specialization of the developed tools in regards to supported
build environments and targeted information.

@@

% TODO QUESTION Somehow, we have to find a better place for this.
%We have been
% using the term 'chunk retrieval' beforehand already -- this
% definition now comes to late.
%The first paragraph should already
% apply to the literature mapping, the second of course only applies
% here.

@@

% Moritz: The following is very obvious and could apply
% to any
% % technique.
% % kinda.
% It does give a descriptive error message on no match (and
% % that is not possible in other techniques)
% % otherwise yes, nothing interesting happens in the application of pbe
% % though for consistency we might need this section? or merge
% config/application?
% Why does it return an error message? Shouldn't it also return
% <empty string>? Does it not rather return an error message if no
% program can be synthesized?
% TODO Moritz: a regular expression can match an empty string
% and that is different from not finding a match
% it returns error messages in both cases
\subsubsection{Application}
A run of PBE takes a build log file as input and applies the
synthesized regular expression program.
It then returns the substring
of the build log matched by the program or an error message if the
program found no match.

@@

\begin{simplebox}[minipage boxed title*=-1.5cm,
attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ2:} What are the comparative strengths and weaknesses
of promising build log analysis techniques?}
\begin{itemize}[leftmargin=1.2cm]
  \item[\textbf{RQ2.1:}] How many examples does a technique need to
  perform best?
  \item[\textbf{RQ2.2:}] How structurally similar do the examples
  need for a technique to be applicable?
  \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
\end{itemize}
\end{simplebox}

@@

When the training examples are of the same structure, one or two
two training examples are enough input for PROSE to synthesize a regular
expression program with good recall.
In the study, additional training
examples from the same structural category
did not improve the chunk retrieval.
% TODO QUESTION: maybe discuss this
% Moritz: Why uncomment the following? Is it not true?
% I think it is crucial.
% In fact, unless they
% were in some sense redundant, adding training examples above that even
% hindered the applicability of PBE.
% TODO: it's true.
% Though this is because of the structural categories
% which we discuss not in this paragraph but the one above.

@@

\textbf{Few Samples with Many Structural Categories}
Our comparison study shows fewer measurements with many structural
categories than with one structural category category
(50.25\% one, 33.75\% two, 13.75\% more than two).
This stems from the fact that we investigated the chunk retrieval
techniques on a real-world data set, where there were mostly few
structural categories within one project.
In addition, a third of the measurements were conducted with two
structural categories present and these already showed the negative
effect of the number of structural categories on the performance
of the chunk retrieval techniques.

@@

\section{Conclusion}
\label{sec:conclusion-fw}
% TODO CARO conclusion should be a bit longer and a little bit more in
% detail.
%Mention general accuracy measures (techniques performed
% up to in F1 score, which is x times better than RLR)
% TODO could also mention future research here: Finally, we gave an
% outline to guide future research efforts in the area of build log
% analysis.
The goal of this paper was to support researchers and developers in
their decision on how to analyze build logs.
To this end, we conducted a systematic mapping study to uncover the
state-of-research on build log analysis.
We implemented three promising chunk retrieval techniques and
compared their performance on the \emph{LogChunks} data set.
Our results show that the structural
representation of the targeted information in the build logs is the
main factor to consider when choosing a suitable technique.
Secondary
factors are the desired confidence into recall and precision of the
produced output and whether precision or recall is more important for
the task at hand.

>>>>

\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
2}}
How do build log analysis techniques compare against each other?
\end{simplebox}

@@

This lead us to the following research questions:
\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ1:} What is the state-of-the-research on analyzing build logs?}
% TODO (resolved): All of these are passive
% TODO Swap RQ 1.2 and RQ 1.1 (logical order?)
\begin{itemize}[leftmargin=2cm]
  \item[\textbf{RQ1.1:}] Which information in build logs is of interest?
  \item[\textbf{RQ1.2:}] Which extraction techniques exist?
  \item[\textbf{RQ1.3:}] Which kinds of build logs are subject to analysis?
\end{itemize}
\end{simplebox}

@@

% TODO: draw a conclusion together with figure 5: if reuse were higher,
%lots of effort could be saved?
We observed very little reuse of build log analysis tools.
This can stem from the
high specialization of the developed tools in regards to supported
% TODO: build environments is used a bunch (also in the following), but
% never defined.
build environments and targeted information.

@@

% TODO QUESTION Somehow, we have to find a better place for this.
%We have been
% using the term 'chunk retrieval' beforehand already -- this
% definition now comes too late.
%The first paragraph should already
% apply to the literature mapping, the second of course only applies
% here.

@@

% Moritz: The following is very obvious and could apply
% to any
% % technique.
% % kinda.
% It does give a descriptive error message on no match (and
% % that is not possible in other techniques)
% TODO Caro: Can you given an example of such an error message?
% % otherwise yes, nothing interesting happens in the application of pbe
% % though for consistency we might need this section? or merge
% config/application?
% Why does it return an error message? Shouldn't it also return
% <empty string>? Does it not rather return an error message if no
% program can be synthesized?
% TODO Moritz: a regular expression can match an empty string
% and that is different from not finding a match
% it returns error messages in both cases
% TODO: Ok, but what is the point of matching on an empty string (if I understand what you mean)? you would not normally define such an extraction?
% If this distinction is important it needs to be made more clear 
\subsubsection{Application}
A run of PBE takes a build log file as input and applies the
synthesized regular expression program.
It then returns the substring
of the build log matched by the program or an error message if the
program found no match.

@@

\begin{simplebox}[minipage boxed title*=-1.5cm,
attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ2:} How do build log analysis techniques compare against each other?}
\begin{itemize}[leftmargin=1.2cm]
  \item[\textbf{RQ2.1:}] How many examples does a technique need to
  perform best?
  \item[\textbf{RQ2.2:}] How structurally similar do the examples
  need for a technique to be applicable?
  \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
\end{itemize}
\end{simplebox}

@@

When the training examples are of the same structure, one or two
two training examples are enough input for PROSE to synthesize a regular
expression program with good recall.
In the study, additional training
examples from the same structural category
did not improve the chunk retrieval. In fact, unless they
were in some sense redundant, adding more training examples even
hindered the applicability of PBE.

@@

\textbf{Few Samples with Many Structural Categories.}
Our comparison study shows fewer measurements with many structural
categories than with one structural category category (50.25\% one,
33.75\% two, 13.75\% more than two).  This stems from the fact that we
investigated the chunk retrieval techniques on a real-world data set,
where there were mostly few structural categories within one project.
In addition, the third of the measurements we conducted with two
structural categories already showed the negative effect of an
increasing number of structural categories on the performance of the
chunk retrieval techniques.

@@

\section{Conclusion}
\label{sec:conclusion-fw}
% TODO CARO conclusion should be a bit longer and a little bit more in
% detail.
%Mention general accuracy measures (techniques performed
% up to in F1 score, which is x times better than RLR)
% TODO could also mention future research here: Finally, we gave an
% outline to guide future research efforts in the area of build log
% analysis.
The goal of this paper is to support practitioners and researchers in
their decision on how to analyze build logs. To this end, we first
conducted a systematic mapping study to map out the available build
log analysis techniques.  We then
implemented three promising chunk retrieval techniques and compared
their performance on the \emph{LogChunks} data set.  Our results show
that the structural representation of the targeted information in the
build logs is the main factor to consider when choosing a suitable
technique.  Secondary factors are the desired confidence in recall and
precision of the produced output and whether precision or recall is
more important for the task at hand.

### 2020-04-24 tse-paper/paper.tex
easy fixes and prio
Inline abstract

\author{Carolin~Brandt,%~\IEEEmembership{Member,~IEEE,}
        Moritz~Beller%~\IEEEmembership{Fellow,~OSA,}% <-this % stops a space
% \IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department
% of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
% GA, 30332.\protect\\
% % note need leading \protect in front of \\ to get a newline within \thanks as
% % \\ is fragile and will error, could use \hfil\break instead.
% E-mail: see http://www.michaelshell.org/contact.html
% \IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops an unwanted space
\thanks{Manuscript received May 1, 2020; revised August 26, 2015.}}

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
\input{abstract.tex}
\end{abstract}

>>>>

\author{Carolin~E.~Brandt, %~\IEEEmembership{Member,~IEEE,}
        Moritz~Beller%~\IEEEmembership{Fellow,~OSA,}% <-this % stops a space
% \IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell was with the Department
% of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
% GA, 30332.\protect\\
% % note need leading \protect in front of \\ to get a newline within \thanks as
% % \\ is fragile and will error, could use \hfil\break instead.
% E-mail: see http://www.michaelshell.org/contact.html
% \IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops an unwanted space
\thanks{Manuscript received May 1, 2020; revised August 26, 2015.}}

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Build logs are the textual by-products that automatic software build processes
create, often as part of their Continuous Integration (CI)
pipeline.
Build logs can serve as a paramount source of
information for developers to understand and debug depdency, compilation, or
test failures.
Manually
extracting the important chunks of information in a build log, though, is akin to
finding a needle in a haystack.
Recently, practitioners and researchers have started attempts to partly
automate
this time-consuming activity, to not only ease
developers' task of finding this needle but also to enable a novel class of
automated on-ward processing applications.
In this paper, we give a systematic overview of the emerging field of build log analysis.
In a large-scale literature mapping study, we first survey and categorize the existing methods to
extract information chunks from build logs.
In the second part of the paper, we develop prototypical implementations of the three most promising
techniques we found, namely program synthesis
by example, textual similarity, and keyword search.
Finally, we evaluate the techniques in an empirical study on
the \emph{LogChunks} data set, which comprises 797 build logs 
from a wide range of different projects and programming languages.
Our findings show that none of the three techniques in general outperforms
the others, but rather, that each technique has its respective strengths
and weaknesses.
We discuss under which circumstances each technique performs best
and provide a recommendation scheme for when developers or researchers might 
use which technique.
We close with a roadmap of important open problems in the
emerging field of
build log analysis.
\end{abstract}
